A Partitioning Algorithm for Maximum Common Subgraph Problems

### 2017-05-18 paper/paper.tex
Expanded caption to give an example of what labels mean

    \caption{Mapping $M$ and vertex labels during search on example graphs $\graphG$ and $\graphH$ from \cref{fig:alg1}.}
    \label{figure:mcsplit-examples}
\end{figure}

>>>>

    \caption{Mapping $M$ and vertex labels during search on example graphs $\graphG$ and
    $\graphH$ from \cref{fig:alg1}.  Labels represent adjacencies; for example, the label
    101 on vertex $e$ in the final table signifies that $e$ is adjacent to the first
    and third mapped vertices of $\graphH$ ($a$ and $f$) but not adjacent to the second
    mapped vertex ($d$).}
    \label{figure:mcsplit-examples}
\end{figure}
